Market Simulator

### 2020-08-25 analysis/05_market_simulator.Rmd
Changed a travel to developing county input
Added Persona naming inputs and added legend for interrepting the Plotly easier

  df[,2] <- c(input$ai_id, input$gp_id, input$ox_id, input$rc_id)
  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
  df[,4] <- c(rep("Persona 1",8), rep("Persona 2", 8), rep("Persona 3", 8))

@@

  ggplotly(df %>% filter(Type == "Market Share") %>% 
             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
             geom_bar(position = "dodge", stat = "identity") +
             labs(x="") + 
             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
             theme(legend.position = "none")
    )
})

@@

@@

@@

@@

>>>>

  df[,2] <- c(input$ai_id, input$gp_id, input$ox_id, input$rc_id)
  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
  df[,4] <- c(rep(input$p1_id,8), rep(input$p2_id, 8), rep(input$p3_id, 8))

@@

  ggplotly(df %>% filter(Type == "Market Share") %>% 
             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
             geom_bar(position = "dodge", stat = "identity") +
             labs(x="") + 
             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
             theme(legend.position = "right")
    )
})

@@

textInput("p1_id",
          label = "Persona Name",
          value = "Persona 1",
          placeholder = "Enter Persona Name")

@@

selectInput("p1_travel_developing",
         label = "Travel to developing country:",
         choices = c("Yes", 'No' = "No Travel to Developing Countries"))

@@

textInput("p2_id",
          label = "Persona Name",
          value = "Persona 2",
          placeholder = "Enter Persona Name")

@@

textInput("p3_id",
          label = "Persona Name",
          value = "Persona 3",
          placeholder = "Enter Persona Name")
